\chapter{Fastype - Gamification of \ac{ned}}
\label{chap:gamechapter}
%Intro to the chapter
In the previous chapter we presented the named entity disambiguation framework which has been implemented as the initial part of the work conducted for this research study. The results after conducting a user study by using a plain interface which we called the AnnotateMe Interface indicate that non-expert users are able to perform qualitative annotations with the help of short contextual clues and an intuitive user interface. However, results also indicated seldom levels of frustration during the experiment in addition to a slight percentage feeling indifferent/neutral towards being engaged or positively motivated in performing the task. For the long-term run, we assume that the plain interface lacks elements of engagement and does not have any associated intrinsic motivation that will bring users back to perform annotations. We hypothesize that by gamifying the system appropriately, it will be possible to increase user engagement with the annotation task and thus increase intrinsic motivation for participation.\if If we manage to intrinsically motivate the users with the game design elements integrated in the annotation task than we are able to claim that it is possible to retain users for a long period of time which makes it possible to generate large-scale annotation corpora.\fi In this chapter we provide an outline of related gamified systems in the field of semantic web and natural language processing (\ac{nlp}) and background information on specific game design and theoretical models on which we base or work. The chapter proceeds by explaining the methodology used from the game implementation, preparation for the second user study and the metrics and assessment techniques used to analyze the data and report on the results. 

\input{game/background}
\input{game/related_work}
\input{game/game_design}
\newpage
\input{game/methodology}
\newpage
\input{game/results}