\subsection{Social Interaction \& Engagement Loop}
%SHoutouts, challanging, desire to compete (being the first in the board) each other as relatedness factors - increasing social interaction - Relatedness is a factor that positively affects intrinsic motivation
Significant design and implementation effort was put in making the game as much socially interactive as possible. Among the three SDT elements which have direct impact in intrinsic motivation and needs satisfaction, social interaction contributes to the feeling of relatedness with others. The main social interaction mechanism implemented in the current version of the game are challenges. The desire to compete and overcome players in the leaderboard can be seen as an element that entails social interaction within the game. 

%engagement loop
The concept of engagement loop on the other hand is a fundamental aspect that needs to be clearly defined in order to maintain player motivation. A successful designed engagement loop always leaves something incomplete or pending in the game for players to come back and play. Game designer David Perry suggests that the key to addictive game design is by creating a game that keeps the player engaged by doing three things all at the time: exercising a skill, taking risks and working out a strategy \cite{15}. Zicherman et al. \cite{48} gives substantial importance to the social engagement loop and defines the following four key aspects to be considered by game designers when thinking about engagement loops: motivating emotion, player re-engagement, social call to action and visible progress/rewards. Table \ref{tab:engagement-loop} lists the game elements of Fastype that contribute to the different aspects of social engagement loop.

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Game elements of Fastype that contribute to the social engagement loop}
    \begin{tabular}{|c|l|}
    \toprule
    \multicolumn{2}{|c|}{Social Engagement Loop} \\
    \midrule
    \multirow{Motivating Emotion} & Excercising fast typing \\
          & Competing with others \\
          & Learning new facts  \\
          & Improving Memory skills \\
    \midrule
    \multirow{Player Renegagement} & Levels \\
          & Challenges  \\
          & Increasing WPM  \\
          & Completing Categories \\
    \midrule
    \multirow{Social call to action} & \multirow{Challenges } \\
          &  \\
    \midrule
    \multirow{Visible progress} & Leaderboard \\
          & Points  \\
          & Levels  \\
          & Challenge Win/Lose Ratio \\
    \bottomrule
    \end{tabular}%
  \label{tab:engagement-loop}%
\end{table}%